Revisiting 'Growth and Inequality in Public Good Provision' ---Reproducing and Generalizing Through Inconvenient Online Experimentation

### 2023-06-12 analysis/quarto/paper.qmd
June2023 State

---
title: Revisiting 'Growth and Inequality in Public Good Provision' ---Reproducing and Generalizing Through Inconvenient Online Experimentation
author:
  - name: Hauke Roggenkamp
    email: hauke.roggenkamp@unisg.ch
    affiliations:
        - id: HSU
          name: Helmut Schmidt University
          department: Department of Economics
          address:  Holstenhofweg 85
          city: Hamburg
          state: Germany
          postal-code: 22043
        - id: HSG
          name: University of St. Gallen
          department: Institute for Behavioral Science and Technology
          address: Torstrasse 25
          city: St. Gallen
          state: Switzerland
          postal-code: 9000
    # attributes:
    #     corresponding: true
    # note: This is the first author footnote.
abstract: |
  I revisit the dynamic public goods game developed by Gächter et al. (2017) to study cooperation under dynamic interdependencies. Collecting data from both a convenient (students) and an inconvenient (general population) sample, I not only reproduce some of the author's original observations but also test their novel game's generalizability. Appending a charitable dictator game, I find no correlations between behavior in the charitable context and the dynamic game. This applies to students and the general population sample alike. Because the study of inexperiend general population samples raises methodological challenges, such as fatigue and dropouts, this research approaches them. Doing so, I provide simple solutions to run relieable interactive experiments online.

  You can find the most recent version of this paper [here](https://github.com/Howquez/coopUncertainty/blob/main/analysis/quarto/paper.pdf).
keywords: 
  - Replication study
  - Non-convenience sample
  - Open science
  - Dynamic public goods game
  - Online experiment
  - Generalizability
date: last-modified
bibliography:  ../biblio.bib
format:
  elsevier-pdf:
    keep-tex: true
    journal:
      name: Journal of Behavioral and Experimental Economics
      formatting: preprint
      model: 3p
      cite-style: authoryear
---

@@

Today's actions are tomorrow's result. There are many settings in which current decisions affect future outcomes and with it, future decision spaces. Opting for environmental friendly policies today not only reduces carbon dioxide omissions immediately but also helps us to reach the Paris climate targets tomorrow. Deferring these policies, may not necessarily prevent us from reaching these targets, but it requires more effort in the future compared to a path that includes immediate action. Aiming at certain goals, today's actions (or the omission thereof) not only affect intermediate outcomes but also the number of paths one can choose from that lead to that specific goal.

@@

A game designed by Gächter, Mengel, Tsakas & Vostroknutov [-@GMTV2017 hereafter, GMTV] as well as Stefan Große (2011, unpublished) shows that it is fairly simple to remedy that limitation. They incorporated interdependencies into a _dynamic_ public goods game (dPGG) by defining endowments as the income of previous periods. To put it differently, participants' actions in a given period affect their number of actions in subsequent periods: the more (less) they earn now, the more (less) they can contribute in the next period. Importantly, this modification qualitatively yields the same rational predictions as the static game (i.e. free-riding and the under-provision of the public good). It is thus, equally well suited to study dilemma situations.

Because there is surprisingly little experimental research on interdependencies^[One exemption are @Moser2019, who built on GMTV's design to investigate leadership.], I reproduced one of GMTV's treatments to compare dynamics across (in)experienced samples to investigate its generalizability.
@GKLS2020 find that static public goods games do not generalize well to real-world climate action. They also find that generalizability depends on structural resemblance of the public goods game with the context of climate change mitigation: Greater resemblance improves generalizability. Because GMTV's dynamic setting has a more realistic property—namely, interdependencies—one would expect it to be better suited to inform public policy. To test this intuition, I not only ran the experiment with different samples but also
<!--, that is, with participants who make their decisions in an environment which is more natural than the lab.-->
observed the participants' behavior in voluntary climate actions (VCA).^[The VCA is a (charitable) dictator game where each participant is a dictator dividing her budget between herself and some organization linked to the reduction of CO2 emissions. @EckelGrossman1996 were the first to implement a charitable dictator game observing contributions of 30% of the endowments. Like @GKLS2020, @CarpenterEtAl2008 report that students make lower contributions to charity than community members.] This yielded a setting similar to @GKLS2020's which allows me to analyze how behavior in the abstract game translates into real-world action across samples. This research shows that the dynamic setting _does not_ add any advances with respect to generalizability of results.

@AGM2018 conducted static public goods games in the lab and on MTurk to draw lessons from online experimentation. This study extends this literature [see, e.g., @SnowbergYariv_2021; @GuptaRigottiWilson_2021; @GoodmanPaolacci2017; @AmirEtAl2012] by focusing on an _inconvenient_ sample (i.e. one that is completely inexperienced sample that has not been exposed to interactive experiments before) playing a computationally more complex game. This required me to design a robust (and thus, more complex) software to minimize attrition. I collected paradata to assess the desired fluency and feasibility of the experiment. This research reports on the robust design that made the dynamic game feasible.

Taken together, this study makes three contributions. First, it reproduces parts of GMTV's original experiment and highlights the importance of pure replications. Second, it shows that logistically complex online experiments are feasible for samples other than students or clickworkers. Third, this paper supports critics arguing that findings from abstract games do not generalize well---not even with a more representative sample.

After commenting on transparent research practices and reporting the methods in @sec-transparency and @sec-methods, this paper is organized along these findings: The confirmatory reproduction is reported in @sec-replication, the online feasibility in @sec-feasibility and the generalizability in @sec-generalizability. @sec-conclusion concludes. Because I observed some differences in reproducing GMTV's analysis using their data, I report these in the [Appendix](@sec-appendix).

@@

In the terminology of @Hamermesh2007, I ran both a _pure_ as well as a _scientific_ reproduction^[@Parsons2022 use the term of a _conceptual replication_ which means the same.] of one treatment of GMTV's dynamic public goods game. The pure reproduction re-analyzes the original data. [Appendix A](#A:-Pure-Replication) documents [errors I identified]() in the original paper. The scientific reproduction, where I utilize a different sample drawn from a different population in a different situation, is described in the following sections.

@@

Considering the design, the only differences between such a _static_ game (with partner matching) and GMTV's design are _dynamics_: Instead of receiving fresh endowments every period, participants receive one endowment only at the beginning of the first period. A participant's endowment in the second period is the wealth she accumulated in the first period. A participant's endowment in the third period is the wealth she accumulated in the first two periods. And so on. Hence, a decision in one period has consequences on future endowments and, ultimately, growth paths. For this reason, the game is described as a _dynamic_ public goods game.

@@

Like GMTV I employ a real giving task after the abstract game. Specifically, I employed a (charitable) dictator game where each participant is a dictator dividing her budget between herself and some organization. Whereas GMTV chose _Doctors without Borders_ as a receiver, I chose another organization in another context: like @GKLS2020, I employed a VCA, where participants could donate any amount their earnings to offset carbon dioxide (that is, retire emission permits from the EU ETS).^[Importantly, @GKLS2020 made the VCA decision with a fresh endowment _before_ they played the abstract game. I deviate from their procedure to match GMTV's procedure.]
To ensure that each participant had the same basic level of information about the impact of their decision, I provided some basic information about the mechanism. The information also highlighted that the mitigation came into operation on a European level.
Finally, I informed the participants that the documentation of individual and aggregate contributions were to be posted immediately after the concluding the sessions online. To avoid privacy or social image concerns, participants learned their unique and random IDs, which they needed to identify their individual contributions.
The document certified that their contributions have been used to offset [1.82 tons](https://www.compensators.org/compensatelist/?searchterm=stefan+traub) of carbon dioxide emissions.

@@

Throughout this paper, I will compare results of my experiment with the results of GMTV's NOPUNISH 10 Period treatments. I am thus, referring to three different samples utilized at two points in time: the University of Nottingham's students (in late 2012), Hamburg's citizens and the University Hamburg's students (both in July 2021). @tbl-sample-properties gives an overview.

@@

vtable::sumtable(data = covs, 
                 vars = c('age', 'gender', 'switching_row'),
                 group = 'sample',
                 group.test = TRUE,
                 digits = 2,
                 labels = c('Age', 'Female', 'Switching Row'),
                 # note = "Switching Row describes choices in a multiple price list to elicit risk preferences. The higher the value, the higher the certainty equivalent. Government Responsible is self-reported based on a question adapted from GMTV ('The government should take responsibility that people are better provided for.')",
                 out = 'latex')
```

@@

Participants entered the experiment at appointed times remotely from home. They first saw a welcome screen. After agreeing to the privacy policy, they could proceed to the instructions individually. Having read these instructions, each participant has also seen a demo-screen explaining the user interface. Before proceeding, they had to answer six comprehension questions correctly to avoid confusion in later stages [@FerraroVossler2010]. Subsequently, they saw a waiting screen until they could be matched with three other participants, who have answered the comprehension questions correctly. Once matched, they were exposed to the decision screen over ten periods. At the end of the last period, participants saw results of all periods. Subsequently, they made their VCA decision, before I elicited risk preferences [@HoltLaury2002] and finished with GMTV's questionnaire.

While I stuck to GMTV's protocol as close as possible, I deviated in a few aspects. First, the instructions were German and also covered topics inherent to the online setting (dropouts and bots, for instance). Second, I used another software (oTree instead of zTree) which also affected the graphical user interface participants were exposed to. Third, GMTV gave participants the opportunity to donate to _Doctors without Borders_ whereas I offered carbon dioxide offsets.

@@

rs1 <- wilcox.test(replication, 
                   GMTV,
                   exact = FALSE)$p.value %>% 
  round(digits = 4) %>% 
  formatC(format = "f", 
          digits = 4)
```

@@

```{r}
for(r in 1:10){
  a <- main[round == r & treatment == 'replication', share]
  b <- main[round == r & treatment == 'noPunish10', share]

  wilcox.test(a, 
              b,
              exact = FALSE)$p.value %>% 
    round(digits = 4) %>% 
    formatC(format = "f", 
            digits = 4)# %>%
    # print()
  }

r <- 5
a <- main[round == r & treatment == 'replication', contribution]
b <- main[round == r & treatment == 'noPunish10', contribution]

@@

```{r plotShareOfContributions}
#| fig-cap: "The average amount of tokens contributed over time in treatments."
#| label: fig-share-of-contributions

@@

rs1 <- wilcox.test(replication, 
                   GMTV,
                   exact = FALSE)$p.value %>% 
  round(digits = 4) %>% 
  formatC(format = "f", 
          digits = 4)

@@

Although there clearly is growth, groups do not realize the maximal potential efficiency: under full cooperation, a group can accumulate at least `r (80*1.5^10) %>% trunc()` tokens or EUR `r (80*1.5^10 /20) %>% trunc()`. This is depicted in the left panel of @fig-growth-heterogeneity, where one can see the average wealth over time by sample. The panel illustrates for both samples that growth was continuous and surprisingly linear, given the exponential character of the game's design. Despite somewhat differing contribution behavior between samples, neither the eventual wealth nor the corresponding growth paths differed. Differences in contribution behavior did, thus, not translate to significantly different wealth outcomes.

@@

Throughout this section, I do not consider GMTV's data and pool data I gathered from the citizens as well as the students from Hamburg (N = `r N`).

@@

How did the participants, who have never participated in an online group experiment before, cope with the situation? Moreover, did participants understand the unfamiliar setting they found themselves in? While the answer to the former question requires more thought, the answer to the latter simply is _yes_: `r 67` out of `r 44 + 67 + 5` answered with _"yes"_ when I asked them. Another `r 44` answered with _"rather yes"_ while nobody indicated that he or she did not understand the situation at all. There is some behavioral data supporting this finding: The user interface offered a popup to review instructions or contact information. I tracked both and find that none of the participants ever opened these popups even though they were clearly visible in the decision screen's header and introduced in the instructions. To further analyze how participants coped with the situation, I consider three additional metrics: selection into the experiment, attrition as well as the time spent on each page.

@@

@GKLS2020 asked how much can we learn about voluntary climate action from the behavior in public goods games. Using a similar strategy, I answer the question for a _dynamic_ public goods game: _Not much_. Overall, there seems to be no association between choices in the voluntary climate action and the first period in the dynamic public goods game.

```{r vca_differences}
rs1 <- wilcox.test(temp[student == FALSE, donationShare], 
                   temp[student == TRUE, donationShare],
                   exact = FALSE)$p.value %>% 
  round(digits = 4) %>% 
  formatC(format = "f", 
          digits = 4)
```

@fig-kernel-generalizability shows distributions of contributions across both choices for both samples. The top panels illustrate the behavior of the general population sample. The bottom panels illustrate the behavior of the student sample. The left panels show the behavior in the VCA. The right panels show the behavior in first period of the game. A visual inspection shows that (a) mean contributions are positive in both tasks for both samples.^[The same holds true for median contributions.] (b) Furthermore, average contributions are lower in the VCA. (c) In contrast to @GKLS2020's observation, I do not observe a difference between samples in the abstract game's contribution behavior. (d) However, the student's share of income contributed to the VCA is significantly lower than the general population sample's contributions (two-sided rank sum test, p=`r rs1`). Taken together, these aggregate results indicate, that the consistency between tasks is higher for the general population than it is for students. Or, to put it differently, the general population's behavior in the abstract game better predicts their behavior in real-world mitigation context.

@@

The initial goal of the experiment was to reproduce specific experiments of GMTV in an online setting using a general population sample. The results suggest that it is important to reproduce experiments---both purely and scientifically [@Hamermesh2007 p. 716]---before drawing conclusions about generalizability.

The three most important findings are as follows: First, the contribution behavior in my experiment is statistically similar to the behavior reported in the original study. Consequently, the outcomes growth and inequality are reproducible. Second, the online experiment proceeded fluently such that dropouts were no concern. Third, contribution behavior in the dynamic abstract setting is not linked to behavior in the real world -- neither for students nor a more representative sample.

@@

Limitations?

@@

<!--
# B: TITLE (exploratory) {.appendix}

Lorem ipsum dolor sit amet, consectetur adipiscing elit. Donec suscipit eleifend felis et faucibus. Curabitur nisl risus, tincidunt ut hendrerit sed, sollicitudin eget tortor. Curabitur tortor elit, finibus a commodo eget, auctor vel dui. Ut convallis, felis in commodo bibendum, ligula neque hendrerit eros, eu eleifend libero ligula pretium dui. Nullam blandit a tellus vitae suscipit. Donec ac justo vehicula elit tincidunt mollis nec ac lectus. Nunc dignissim sem eu felis consequat, id euismod ante imperdiet. Mauris quis ex ante.

Nulla elementum laoreet libero nec consequat. Donec blandit, tellus id feugiat viverra, lectus tellus sollicitudin ipsum, ut venenatis nunc mauris ut arcu. Donec mi eros, ullamcorper aliquet varius non, cursus vel lorem. Integer feugiat dui sapien, ac porta lacus porta sit amet. Aliquam interdum dictum tempor. Quisque bibendum feugiat scelerisque. Sed eu purus eu est ullamcorper bibendum.

Donec efficitur magna malesuada tortor feugiat tristique. Sed porttitor, quam at vulputate placerat, elit magna posuere est, a eleifend lacus magna ac nunc. Quisque sit amet arcu mattis, malesuada mauris et, aliquam libero. Fusce viverra sed dolor a ullamcorper. Aliquam in ligula neque. In maximus nisl id ante vehicula, et euismod ante feugiat. Suspendisse et dui lectus. Ut euismod ultrices mi eu lacinia.

```{r firstRoundVizAppendix}

d1 <- ggplot(data = R1[treatment == "replication"],
       mapping = aes(x = ownContribution, fill = student, lty = student)) +
  geom_density(alpha = 0.5) +
  scale_x_continuous(limits = c(0, 20),
                       expand = c(0, NA)) +
  scale_y_continuous(limits = c(0, 0.1),
                       expand = c(0, NA)) +
  scale_fill_manual(values = c(cPrimary, cSecondary),
                    labels = c("General Population Sample", "Student Sample")) +
  guides(lty = "none") +
  geom_vline(xintercept = R1[treatment == "replication", 
                             mean(ownContribution)],
             col = "#FFFFFF",
             lty = 2) +
  geom_vline(xintercept = R1[treatment == "noPunish10", 
                             mean(ownContribution)],
             col = "#FFFFFF",
             lty = 1) +
    labs(title = "", 
       y = "", x = "Initially Contributed Tokens") +
  layout +
  theme(legend.position = "top")
```

```{r stockDistributionVizAppendix}

populationWealth <- main[treatment == "replication" & student == FALSE & round == 10,
                         mean(stock)]
studentWealth    <- main[treatment == "replication" & student == TRUE & round == 10,
                         mean(stock)]

d2 <- ggplot(data = main[treatment == "replication"],
       mapping = aes(x = stock, fill = student, lty = student)) +
  geom_density(alpha = 0.5) +
  scale_x_continuous(limits = c(0, NA),
                       expand = c(0, NA)) +
  scale_y_continuous(limits = c(0, NA),
                       expand = c(0, NA)) +
  scale_fill_manual(values = c(cPrimary, cSecondary),
                    labels = c("General Population Sample", "Student Sample")) +
  guides(lty = "none") +
  geom_vline(xintercept = studentWealth,
             col = "#000000", alpha = 0.5,
             lty = 2) +
  geom_vline(xintercept = populationWealth,
             col = "#000000", alpha = 0.5,
             lty = 1) +
    labs(title = "", 
       y = "", x = "Stock") +
  layout +
  theme(legend.position = "top")
```

```{r giniDistributionVizAppendix}

populationGini    <- main[treatment == "replication" & student == FALSE & round == 10,
                        mean(gini)] %>% round(digits = 2)
studentGini <- main[treatment == "replication" & student == TRUE & round == 10,
                        mean(gini)] %>% round(digits = 2)

>>>>

---
title: Revisiting 'Growth and Inequality in Public Good Provision' ---Reproducing and Generalizing Through Inconvenient Online Experimentation
author:
  - name: Hauke Roggenkamp
    email: hauke.roggenkamp@unisg.ch
    affiliations:
        - id: HSU
          name: Helmut Schmidt University
          department: Department of Economics
          address:  Holstenhofweg 85
          city: Hamburg
          state: Germany
          postal-code: 22043
        - id: HSG
          name: University of St. Gallen
          department: Institute for Behavioral Science and Technology
          address: Torstrasse 25
          city: St. Gallen
          state: Switzerland
          postal-code: 9000
    # attributes:
    #     corresponding: true
    # note: This is the first author footnote.
abstract: |
  I revisit the dynamic public goods game developed by Gächter et al. (2017) to study cooperation under dynamic interdependencies. Collecting data from both a convenient (students) and an inconvenient (general population) sample, I not only reproduce some of the authors' original observations but also test their novel game's generalizability. Appending a charitable dictator game, I find no correlations between behavior in the charitable context and the dynamic game. This applies to students and the general population sample alike. Because the study of inexperienced general population samples raises methodological challenges, such as fatigue and dropouts, this research approaches them. Doing so, I provide simple solutions to run reliable interactive experiments online.

keywords: 
  - Public goods
  - Dynamic games
  - Reproducibility
  - Generalizability
  - Online Experiment
  - Climate change mitigation
date: last-modified
bibliography:  ../biblio.bib
format:
  elsevier-pdf:
    keep-tex: true
    journal:
      name: Journal of Behavioral and Experimental Economics
      formatting: review
      model: 3p
      layout: onecolumn
      cite-style: authoryear
      highlights:
        - Highlight 1
        - Highlight 2 
        - Highlight 3
---

@@

Today's actions are tomorrow's result. There are many settings in which current decisions affect future outcomes and with it, future decision spaces. 
<!-- Think of lifetime consumption‐smoothing and save more tomorrow -->
Opting for environmental friendly policies today not only reduces carbon dioxide omissions immediately but also helps us to reach the Paris climate targets tomorrow. Deferring these policies, may not necessarily prevent us from reaching these targets, but it requires more effort in the future compared to a path that includes immediate action @HaenselEtAl2022. Aiming at certain goals, today's actions (or the omission thereof) not only affect intermediate outcomes but also the number of paths one can choose from that lead to that specific goal.

@@

A game designed by Gächter, Mengel, Tsakas & Vostroknutov [-@GMTV2017 hereafter, GMTV] as well as Stefan Große (unpublished) shows that it is fairly simple to add this element of realism. They incorporate interdependencies into a _dynamic_ public goods game (dPGG) by defining endowments as the income of previous periods. Consequently, participants' actions in a given period affect their number of actions in subsequent periods: the more (less) they earn now, the more (less) they can contribute in the next period. Importantly, this modification qualitatively yields the same rational predictions as the static game (i.e. free-riding and the under-provision of the public good). It is thus, equally well suited to study dilemma situations.

Because there is surprisingly little experimental research on interdependencies^[One exemption are @Moser2019, who built on GMTVs' design to investigate leadership.], I reproduced one of GMTVs' treatments to compare dynamics across (in)experienced samples to investigate its generalizability.
@GKLS2020 find that static public goods games do not generalize well to real-world climate action. They also find that generalizability depends on structural resemblance of the public goods game with the context of climate change mitigation: Greater resemblance improves generalizability. Because GMTVs' dynamic setting has a more realistic property—namely, interdependencies—one would expect it to be better suited to inform public policy. To test this intuition, I not only ran the experiment with different samples but also
<!--, that is, with participants who make their decisions in an environment which is more natural than the lab.-->
observed the participants' behavior in voluntary climate actions (VCA).^[The VCA is a (charitable) dictator game where each participant is a dictator dividing her budget between herself and some organization linked to the reduction of CO2 emissions. @EckelGrossman1996 were the first to implement a charitable dictator game observing contributions of 30% of the endowments. Like @GKLS2020, @CarpenterEtAl2008 report that students make lower contributions to charity than community members.] This yielded a setting similar to the one of @GKLS2020, which allows me to analyze how behavior in the abstract game translates into real-world action across samples. This research shows that the dynamic setting _does not_ add any advances with respect to generalizability of results.

@AGM2018 conducted static public goods games in the lab and on MTurk to draw (and report) lessons from online experimentation. This study extends this literature [see, e.g., @SnowbergYariv_2021; @GuptaRigottiWilson_2021; @GoodmanPaolacci2017; @AmirEtAl2012] by focusing on an _inconvenient_ sample (i.e. one that is completely inexperienced sample that has not been exposed to interactive experiments before) playing a computationally more complex game. This required me to design a robust (and thus, more complex) software to minimize attrition. I collected paradata---which captures screen time and survey navigation, for instance---to assess the desired fluency and feasibility of the experiment. Like @AGM2018, this research is of practical relevance as it reports on the robust design that made the dynamic game feasible.

Taken together, this study makes three contributions. First, it reproduces parts of GMTVs' original experiment and highlights the importance of pure replications. Second, it shows that logistically complex online experiments are feasible for samples other than students or clickworkers. Third, this paper supports critics arguing that findings from abstract games do not generalize well---not even with a more representative sample.

After commenting on transparent research practices and reporting the methods in @sec-transparency and @sec-methods, this paper is organized along these findings: The confirmatory reproduction is reported in @sec-replication, the online feasibility in @sec-feasibility and the generalizability in @sec-generalizability. @sec-conclusion concludes. Because I observed some (qualitatively inconsequential) differences in reproducing GMTVs' analysis using their data, I report these in the [Appendix](@sec-appendix).

@@

In the terminology of @Hamermesh2007, I ran both a _pure_ as well as a _scientific_ reproduction^[@Parsons2022 use the term of a _conceptual replication_ which means the same.] of one treatment of GMTVs' dynamic public goods game. The pure reproduction re-analyzes the original data. [Appendix A](#A:-Pure-Replication) documents [errors I identified]() in the original paper. The scientific reproduction, where I utilize a different sample drawn from a different population in a different situation, is described in the following sections.

@@

Considering the design, the only differences between such a _static_ game (with partner matching) and GMTVs' design are _dynamics_: Instead of receiving fresh endowments every period, participants receive one endowment only at the beginning of the first period. A participant's endowment in the second period is the wealth she accumulated in the first period. A participant's endowment in the third period is the wealth she accumulated in the first two periods. And so on. Hence, a decision in one period has consequences on future endowments and, ultimately, growth paths. For this reason, the game is described as a _dynamic_ public goods game.

@@

Like GMTV I employ a real giving task after the abstract game. Specifically, I employed a (charitable) dictator game where each participant is a dictator dividing her budget between herself and some organization. Whereas GMTV chose _Doctors without Borders_ as a receiver, I chose another organization in another context: like @GKLS2020, I employed a VCA, where participants could donate any amount of their earnings to offset carbon dioxide (that is, retire emission permits from the EU ETS).^[Importantly, @GKLS2020 made the VCA decision with a fresh endowment _before_ they played the abstract game. I deviate from their procedure to match GMTVs' procedure.]
To ensure that each participant had the same basic level of information about the impact of their decision, I provided some basic information about the mechanism. The information also highlighted that the mitigation came into operation on a European level.
Finally, I informed the participants that the documentation of individual and aggregate contributions were to be posted immediately after the concluding the sessions online. To avoid privacy or social image concerns, participants learned their unique and random IDs, which they needed to identify their individual contributions.
The document certified that their contributions have been used to offset [1.82 tons](https://www.compensators.org/compensatelist/?searchterm=stefan+traub) of carbon dioxide emissions.

@@

Throughout this paper, I will compare results of my experiment with the results of GMTVs' NOPUNISH 10 Period treatments. I am thus, referring to three different samples utilized at two points in time: the University of Nottingham's students (in late 2012), Hamburg's citizens and the University Hamburg's students (both in July 2021). @tbl-sample-properties gives an overview.

@@

vtable::sumtable(data = covs, 
                 vars = c('age', 'gender', 'switching_row'),
                 group = 'sample',
                 group.test = TRUE,
                 digits = 2,
                 labels = c('Age', 'Female', 'Risk Aversion (1-12)'),
                 # note = "Switching Row describes choices in a multiple price list to elicit risk preferences. The higher the value, the higher the certainty equivalent. Government Responsible is self-reported based on a question adapted from GMTV ('The government should take responsibility that people are better provided for.')",
                 out = 'latex')
```

@@

Participants entered the experiment at appointed times remotely from home. They first saw a welcome screen. After agreeing to the privacy policy, they could proceed to the instructions individually. Having read these instructions, each participant has also seen a demo-screen explaining the user interface. Before proceeding, they had to answer six comprehension questions correctly to avoid confusion in later stages [@FerraroVossler2010]. Subsequently, they saw a waiting screen until they could be matched with three other participants, who have answered the comprehension questions correctly. Once matched, they were exposed to the decision screen over ten periods. At the end of the last period, participants saw results of all periods. Subsequently, they made their VCA decision, before I elicited risk preferences [@HoltLaury2002] and finished with GMTVs' questionnaire.

While I stuck to GMTVs' protocol as close as possible, I deviated in a few aspects. First, the instructions were German and also covered topics inherent to the online setting (dropouts and bots, for instance). Second, I used another software (oTree instead of zTree) which also affected the graphical user interface participants were exposed to. Third, GMTV gave participants the opportunity to donate to _Doctors without Borders_ whereas I offered carbon dioxide offsets.

@@

rs1 <- wilcox.test(replication, 
                   GMTV,
                   exact = FALSE)$p.value %>% 
  round(digits = 3) %>% 
  formatC(format = "f", 
          digits = 3)
```

@@

```{r}
r <- 5
a <- main[round == r & treatment == 'replication', contribution]
b <- main[round == r & treatment == 'noPunish10', contribution]

@@

```{r plotShareOfContributions}
#| fig-cap: "The average amount of tokens contributed over time across samples."
#| label: fig-share-of-contributions

@@

rs1 <- wilcox.test(replication, 
                   GMTV,
                   exact = FALSE)$p.value %>% 
  round(digits = 3) %>% 
  formatC(format = "f", 
          digits = 3)

@@

Although there clearly is growth, groups do not realize the maximal potential efficiency: under full cooperation, a group can accumulate at maximum `r (80*1.5^10) %>% trunc()` tokens or EUR `r (80*1.5^10 /20) %>% trunc()`. This is depicted in the left panel of @fig-growth-heterogeneity, where one can see the average wealth over time by sample. The panel illustrates for both samples that growth was continuous and surprisingly linear, given the exponential character of the game's design. Despite somewhat differing contribution behavior between samples, neither the eventual wealth nor the corresponding growth paths differed. Differences in contribution behavior did, thus, not translate to significantly different wealth outcomes.

@@

Throughout this section, I do not consider GMTVs' data and pool data I gathered from the citizens as well as the students from Hamburg (N = `r N`).

@@

How did the participants, who have never participated in an online group experiment before, cope with the situation? Moreover, did participants understand the unfamiliar setting they found themselves in? While the answer to the former question requires more thought, the answer to the latter simply is _yes_: `r 67` out of `r 44 + 67 + 5` answered with _"yes"_ when I asked them. Another `r 44` answered with _"rather yes"_ while nobody indicated that he or she did not understand the situation at all. There is some behavioral data supporting this finding: The user interface offered a popup to review instructions or contact information. I tracked both and find that none of the participants ever opened these popups even though they were clearly visible in the decision screens' header and introduced in the instructions. To further analyze how participants coped with the situation, I consider three additional metrics: selection into the experiment, attrition as well as the time spent on each page.

@@

@GKLS2020 asked how much can we learn about voluntary climate action from the behavior in public goods games. Using a similar strategy, I answer the question for a _dynamic_ public goods game: _Not too much_. Overall, there seems to be no association between choices in the voluntary climate action and the first period in the dynamic public goods game.

```{r vca_differences}
rs1 <- wilcox.test(temp[student == FALSE, donationShare], 
                   temp[student == TRUE, donationShare],
                   exact = FALSE)$p.value %>% 
  round(digits = 3) %>% 
  formatC(format = "f", 
          digits = 3)
```

@fig-kernel-generalizability shows distributions of contributions across both choices for both samples. The top panels illustrate the behavior of the general population sample. The bottom panels illustrate the behavior of the student sample. The left panels show the behavior in the VCA. The right panels show the behavior in first period of the game. A visual inspection shows that (a) mean contributions are positive in both tasks for both samples.^[The same holds true for median contributions.] (b) Furthermore, average contributions are lower in the VCA. (c) In contrast to the observation of @GKLS2020, I do not observe a difference between samples in the abstract game's contribution behavior. (d) However, the student's share of income contributed to the VCA is significantly lower than the general population sample's contributions (two-sided rank sum test, p=`r rs1`). Taken together, these aggregate results indicate, that the consistency between tasks is higher for the general population than it is for students. Or, to put it differently, the general population's behavior in the abstract game better predicts their behavior in real-world mitigation context.

@@

The initial goal of the experiment was to reproduce specific experiments of GMTV in an online setting using a general population sample. 
<!--The results suggest that it is important to reproduce experiments---both purely and scientifically [@Hamermesh2007 p. 716]---before drawing conclusions about generalizability.
-->
The three most important findings are as follows: First, the contribution behavior in my experiment is statistically similar to the behavior reported in the original study. Consequently, the outcomes growth and inequality are reproducible in both meanings: they are _purely_ (despite minor differences one can re-analyze the original data and reach the same conclusions) and _scientifically_ (one can gather new data drawn from a different population in a different situation and find similar patterns) reproducible. Second, the online experiment proceeded fluently such that dropouts were no concern. Third, contribution behavior in the dynamic abstract setting is not linked to behavior in the real world -- neither for students nor a more representative sample.

@@

Taken together the results answer the questions whether GMTVs' dynamic paradigm is reproducible  across samples (yes) and whether it is feasible employ it online (also yes). The question that is _not_ answered is, whether GMTVs' treatment effects replicate well because I did not focus on treatments and treatment effects. It thus, remains an open question, whether the causal effect of GMTVs' treatments replicate well. Further, we do not know whether their treatments affect real-world behavior. How generalizable are treatment effects in public goods games in general? Albeit this study does not address these questions, it provides methods suited to investigate them---even with inconvenient samples.

# Acknowledgements

I gratefully acknowledge support by the German Research Foundation (DFG) under Germany’s Excellence Strategy, cluster EXC 2037 “Climate, Climatic Change, and Society” (project 390683824). I thank Stefan Traub and participants of the CLICCS B5 group for helpful discussions.

@@

# B: Tables

```{r}
#| label: tbl-contribution-periods
#| tbl-cap: The average amount of tokens contributed over time across samples.

p <- data.table(round = 1:10)
for(r in 1:10){
  a <- main[round == r & treatment == 'replication', contribution]
  b <- main[round == r & treatment == 'noPunish10', contribution]

  p[round == r, `p-value` := wilcox.test(a, b, exact = FALSE)$p.value %>% 
      round(digits = 3) %>% 
      formatC(format = "f", digits = 3)]
}

tmp <- main[, 
            .(Mean = mean(contribution, na.rm = TRUE) %>% formatC(format = "f", digits = 3),
              CI = t.test(contribution, conf.level = 0.95)$conf.int[c(1,2)] %>% formatC(format = "f", digits = 3) %>% paste(collapse = " - ")),
            by = c('treatment', 'round')] %>%
  data.table::dcast(formula = round ~ treatment,
                    value.var = c('Mean', 'CI'))

tmp <- tmp[, c(1,2,4,3,5)]

tmp[p, on = .(round = round)] %>%
  kable(col.names = c('Period', 
                      'Mean: Original', '95%-CI: Original',
                      'Mean: Reproduction', '95%-CI: Reproduction',
                      'p-Value'))

```{r}
#| label: tbl-share-periods
#| tbl-cap: The average share of current endowments contributed over time across samples.

p <- data.table(round = 1:10)
for(r in 1:10){
  a <- main[round == r & treatment == 'replication', share]
  b <- main[round == r & treatment == 'noPunish10', share]

  p[round == r, `p-value` := wilcox.test(a, b, exact = FALSE)$p.value %>% 
      round(digits = 3) %>% 
      formatC(format = "f", digits = 3)]
}

tmp <- main[, 
            .(Mean = mean(share, na.rm = TRUE) %>% formatC(format = "f", digits = 3),
              CI = t.test(share, conf.level = 0.95)$conf.int[c(1,2)] %>% formatC(format = "f", digits = 3) %>% paste(collapse = " - ")),
            by = c('treatment', 'round')] %>%
  data.table::dcast(formula = round ~ treatment,
                    value.var = c('Mean', 'CI'))

tmp <- tmp[, c(1,2,4,3,5)]

tmp[p, on = .(round = round)] %>%
  kable(col.names = c('Period', 
                      'Mean: Original', '95%-CI: Original',
                      'Mean: Reproduction', '95%-CI: Reproduction',
                      'p-Value'))

```{r}
#| label: tbl-wealth-periods
#| tbl-cap: The average wealth over time across samples.

p <- data.table(round = 1:10)
for(r in 1:10){
  a <- main[round == r & treatment == 'replication', stock]
  b <- main[round == r & treatment == 'noPunish10', stock]

  p[round == r, `p-value` := wilcox.test(a, b, exact = FALSE)$p.value %>% 
      round(digits = 3) %>% 
      formatC(format = "f", digits = 3)]
}

tmp <- main[, 
            .(Mean = mean(stock, na.rm = TRUE) %>% formatC(format = "f", digits = 3),
              CI = t.test(stock, conf.level = 0.95)$conf.int[c(1,2)] %>% formatC(format = "f", digits = 3) %>% paste(collapse = " - ")),
            by = c('treatment', 'round')] %>%
  data.table::dcast(formula = round ~ treatment,
                    value.var = c('Mean', 'CI'))

tmp <- tmp[, c(1,2,4,3,5)]

tmp[p, on = .(round = round)] %>%
  kable(col.names = c('Period', 
                      'Mean: Original', '95%-CI: Original',
                      'Mean: Reproduction', '95%-CI: Reproduction',
                      'p-Value'))

```{r}
#| label: tbl-gini-periods
#| tbl-cap: The average Gini coefficient over time across samples.

p <- data.table(round = 1:10)
for(r in 1:10){
  a <- main[round == r & treatment == 'replication', gini]
  b <- main[round == r & treatment == 'noPunish10', gini]

  p[round == r, `p-value` := wilcox.test(a, b, exact = FALSE)$p.value %>% 
      round(digits = 3) %>% 
      formatC(format = "f", digits = 3)]
}

tmp <- main[, 
            .(Mean = mean(gini, na.rm = TRUE) %>% formatC(format = "f", digits = 3),
              CI = t.test(gini, conf.level = 0.95)$conf.int[c(1,2)] %>% formatC(format = "f", digits = 3) %>% paste(collapse = " - ")),
            by = c('treatment', 'round')] %>%
  data.table::dcast(formula = round ~ treatment,
                    value.var = c('Mean', 'CI'))

tmp <- tmp[, c(1,2,4,3,5)]
